\hspace*{-.7em} Analysis of JavaScript Web Applications\\ Using \safe

### 2016-11-18 doc/icse-demo/main.tex
Demo paper

\begin{abstract}
JavaScript has been the language for web applications, and
the growing prevalence of web environments in various devices
makes JavaScript web applications even more ubiquitous.
However, because JavaScript and web environments are
extremely dynamic, JavaScript web applications are often
vulnerable to type-related errors and security attacks.
To lessen the problem, researchers have developed various analysis
techniques in different analyzers, but such analyzers are not especially
aimed for ease of use by analysis developers.  In this paper, we present \safe, a scalable
analysis framework for ECMAScript especially designed as a playground
for advanced research in JavaScript web applications.  \safe is
light-weight, which supports pluggability, extensibility, and
debuggability.
\end{abstract}

@@

\setcounter{figure}{1}
\begin{figure*}[t]
\centering
\begin{tabular}{c}
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
val commands: List[Command] = List(CmdParse, CmdASTRewrite, CmdCompile, CmdCFGBuild, CmdAnalyze,
                                   CmdBugDetect, CmdHelp)
var phases: List[Phase] = List(Parse, ASTRewrite, Compile, CFGBuild, Analyze, BugDetect, Help)
\end{verbatim}
\end{minipage}
\\[1.5em]
{\small (a) Add a new command and a new phase to the lists of available
commands and phases, respectively, in \mtt{Safe.scala}}
\\[1em]
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
case object CmdBugDetect extends CommandObj("bugDetect", CmdAnalyze >> BugDetect) {
  override def display(cfg: CFG): Unit = println(cfg.toString(0))
}
\end{verbatim}
\end{minipage}
\\[1em]
{\small (b) Add the new command by specifying its name and phases in \mtt{Command.scala}}
\\[1em]
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
case object BugDetect extends PhaseObj[(CFG, Int, CallContext), BugDetectConfig, CFG] {
  val name: String = "bugDetector"
  val help: String = "Detect possible bugs in JavaScript source files."
  def apply(in: (CFG, Int, CallContext), safeConfig: SafeConfig, config: BugDetectConfig): Try[CFG] = {
    val (cfg, _, _) = in
\end{verbatim}
\vspace*{-.6em}
\textbf{~~~~~~~// Bug detector implementation here.}
\vspace*{-.8em}
\begin{verbatim}
    Success(cfg)
  }
  def defaultConfig: BugDetectConfig = BugDetectConfig()
  val options: List[PhaseOption[BugDetectConfig]] = List(
    ("silent", BoolOption(c => c.silent = true), "messages during analysis are muted.")
  )
}

case class BugDetectConfig(var silent: Boolean = false) extends Config

\end{verbatim}
\end{minipage}
\\
{\small (c) Implement the new phase in \mtt{phase/BugDetect.scala}}
\end{tabular}
\caption{\small Extension of \safe with a bug detector~\cite{jswapp}}
\label{fig:extensibility}
\end{figure*}

@@

In this paper, we present \safe\footnote{
\url{https://github.com/sukyoung/safe}}, a playground
for advanced research in JavaScript web applications\footnote{
We call SAFE ``\oldsafe'' from now on to distinguish it from \safe.
}.  We designed it to be light-weight, highly parametric,
and modular.  \safe has the following main features:
\begin{itemize}
\item Pluggability: To help analysis developers experiment with
various analysis techniques easily, \safe enables analysis sensitivities
and even abstract domains to be selected at run time.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=.7\textwidth]{htmldebugger.png}
\caption{\htmldebug}\label{fig:htmldebug}
\end{figure*}

>>>>

\begin{abstract}
JavaScript has been the language for web applications, and
the growing prevalence of web environments in various devices
makes JavaScript web applications even more ubiquitous.
However, because JavaScript and web environments are
extremely dynamic, JavaScript web applications are often
vulnerable to type-related errors and security attacks.
To lessen the problem, researchers have developed various analysis
techniques in different analyzers, but such analyzers are not especially
aimed for ease of use by analysis developers.  In this paper, we present \safe, a scalable
analysis framework for ECMAScript especially designed as a playground
for advanced research in JavaScript web applications.  \safe is
light-weight, which supports pluggability, extensibility, and
debuggability.

Demo video: \url{http://youtu.be/x7Jr_gyyHD0}
\end{abstract}

@@

\setcounter{figure}{1}
\begin{figure*}[t]
\centering
\begin{tabular}{c}
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
val commands: List[Command] = List(CmdParse, CmdASTRewrite, CmdCompile, CmdCFGBuild, CmdAnalyze,
                                   CmdBugDetect, CmdHelp)
var phases: List[Phase] = List(Parse, ASTRewrite, Compile, CFGBuild, Analyze, BugDetect, Help)
\end{verbatim}
\end{minipage}
\\[1.5em]
{\small (a) Add a new command and a new phase to the lists of available
commands and phases, respectively, in \mtt{Safe.scala}}
\\[1em]
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
case object CmdBugDetect extends CommandObj("bugDetect", CmdAnalyze >> BugDetect)
\end{verbatim}
\end{minipage}
\\[1em]
{\small (b) Add the new command by specifying its name and phases in \mtt{Command.scala}}
\\[1em]
\begin{minipage}{.95\textwidth}
\footnotesize
\begin{verbatim}
case object BugDetect extends PhaseObj[(CFG, Int, CallContext), BugDetectConfig, CFG] {
  val name: String = "bugDetector"
  val help: String = "Detect possible bugs in JavaScript source files."
  def defaultConfig: BugDetectConfig = BugDetectConfig()
  val options: List[PhaseOption[BugDetectConfig]] = List(
    ("silent", BoolOption(c => c.silent = true), "messages during analysis are muted.")
  )

  def apply(in: (CFG, Int, CallContext), safeConfig: SafeConfig, config: BugDetectConfig): Try[CFG] = {
    val (cfg, _, _) = in
\end{verbatim}
\vspace*{-.6em}
\textbf{~~~~~~~// Bug detector implementation here.}
\vspace*{-.8em}
\begin{verbatim}
    Success(cfg)
  }
}

case class BugDetectConfig(var silent: Boolean = false) extends Config
\end{verbatim}
\end{minipage}
\\
{\small (c) Implement the new phase in \mtt{phase/BugDetect.scala}}
\end{tabular}
\caption{\small Extension of \safe with a bug detector~\cite{jswapp}}
\label{fig:extensibility}
\end{figure*}

@@

In this paper, we present \safe\footnote{
\url{https://github.com/sukyoung/safe}}, a playground
for advanced research in JavaScript web applications\footnote{
We call SAFE ``\oldsafe'' from now on to distinguish it from \safe.
}.  We designed it to be light-weight, highly parametric,
and modular.  \safe has the following main features:
\begin{itemize}
\item Pluggability: To help developers experiment with
analysis techniques easily, \safe enables analysis sensitivities
and even abstract domains to be selected at run time.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=.68\textwidth]{htmldebugger.png}
\caption{\htmldebug}\label{fig:htmldebug}
\end{figure*}
